\begin{itemize}
  \item  ``Staggered Grid Abstractions for Scalable Solvers'', FOALAB Group Meeting, University of Oxford, October 18, 2019.
\item ``\textsc{StagYY} and \textsc{StagBL}: Developing Tools for Large-Scale Geodynamic Simulations Using Staggered-Grid Discretisation on Hybrid Architechtures'', PASC 19 Conference, ETH Zurich, Zurich, Switzerland, June 12-14, 2019.
\item ``Modern Solvers for Global Mantle Convection: \textsc{StagYY} with \textsc{StagBL}'' (PICO presentation), EGU General Assembly, Vienna, Austra, April 8-12, 2019.
\item ``\textsc{DMStag}: A Staggered-grid Abstraction for \textsc{PETSc}'', \textsc{PETSc} Users' Meeting, Imperial College, London, United Kingdom, June 4-6, 2018.
\item ``Hybrid Operators and Composable Software within Lithospheric Dynamic Simulation'', SIAM Conference on Parallel Processing for Scientific Computing, Tokyo, Japan, March 7-10, 2018.
\item ``\textsc{StagBL}: A Scalable, Portable, High-Performance Discretization and Solver Layer for Geodynamic Simulation'', PASC 18 Conference, Basel, Switzerland, July 2-4, 2018.
\item ``GeoPC: Composable Solvers for Geophysics on Modern Architectures'', PASC 17 Conference, Lugano, Switzerland, June 26-28, 2017. [\href{http://patricksanan.com/talks/SANAN_patrick_PASC17.pdf}{slides online}]
\item ``Preconditioners for Stokes Flow with Highly Heterogeneous Viscosity Structure: Saddle-Point Smoothing Via Local Incomplete Factorization'', SIAM CSE, Atlanta, United States, February 27-March 3, 2016.
\item ``Robust Multigrid Solvers For Highly Heterogeneous Stokes Flow,'' Swiss Geoscience Meeting, Geneva, Switzerland, November 18-19, 2016.
\item ``Robust Multigrid Solvers for Geodynamics,'' German-Swiss Geodynamics Workshop, Lichtenfels, Germany, September 11-14, 2016.
\item ``Extreme-scale Multigrid Components within PETSc''
\vspace{-8pt}
\begin{tightitemize}
\item PETSc Users Meeting, Vienna, Austria, June 28-30, 2016.
\item ACM/PASC16 conference, Lausanne, Switzerland, June 8-10, 2016.[\href{http://insidehpc.com/2016/06/extreme-scale-multigrid/}{video online}]
\end{tightitemize}
\begin{samepage}
\item ``Accelerating Parallel Multilevel Solvers for Stokes Flow with Highly Heterogeneous Viscosity Structure: Localized Incomplete $LDL^T$ Smoothers and GPUs'', EGU General Assembly, Vienna, Austria, April 17-22, 2016.
\item ``Co-designing algorithms: Pipelined, Flexible Krylov Subspace Methods and  Accelerated Subdomain Solves''.
\vspace{-8pt}
\begin{tightitemize}
\item SeisMIC, Technical University of Ostrava, Czech Republic, February 5, 2016.
\item Computing Sciences Seminar, Lawrence Berkeley Lab, January 12, 2016.
\end{tightitemize}
\end{samepage}
\item ``Pipelined, Flexible Krylov Subspace Methods and Accelerated Subdomain Smoothing: Attacks on aggressive nested preconditioners for challenging geophysical Stokes flow problems''[minisymposium talk], SIAM Conference on Applied Linear Algebra, Atlanta, Georgia, USA, October 26-30, 2015.
\item ``Towards Aggressive, Accelerated Multigrid Smoothing''[invited talk], ASE Seminar, University of Tokyo, Tokyo, Japan, October 16, 2015.
\item ``Pipelined, Flexible Krylov Subspace Methods''[invited talk], IWACOM-III, Tokyo, Japan, October 12-14, 2015.
\item ``Using Julia on a Cray Supercomputer''[lightning talk], Juliacon 2015, MIT, Boston, Massachusetts, USA, June 24-27, 2015. [\href{https://www.youtube.com/watch?v=NwyKz2KLdtY}{video online}]
\end{itemize}
